---
title: "ThuggerDaily"
author: "Sagnik Chakravarty"
format: html
knitr:
  opts_chunk:
    echo: false
    message: false
    warning: false
---

```{r warning=FALSE, message=FALSE, echo = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(plotly)
library(readxl)
library(stringr)
library(purrr)
library(tidyr)
library(viridis)
library(lubridate)
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
thugger <- read_csv("/Users/sagnikchakravarty/Documents/Young Thug/Data/Cleaned Data/Topic Modeling/Internet/thuggerdaily_twitter.csv")
Timeline <- read_csv("/Users/sagnikchakravarty/Documents/Young Thug/Timeline.csv", 
                     col_types = cols(Date = col_date(format = "%m/%d/%Y")))

thugger <- thugger %>% select(-...1)
```

## Thugger Daily

### Finding engagement Rate

So we need to find the engagement rate, for this I am developing a new variable which takes into analytics, comments, retweet and likes into account assigning weights to each of them,

Comments: 30%

Retweets: 40%

likes: 30%

$$
Engagement = \frac{Likes + Retweets + Comments}{Analytics}\times 100
$$

```{r echo =FALSE}
thugger <- thugger %>% 
  mutate(engagement_score = (0.3*Likes+0.4*Retweets+0.3*Comments)/Analytics *100)
```

```{r echo = FALSE}
thugger_by_day <- thugger %>% mutate(Date = as.Date(Timestamp)) %>%
  group_by(Date) %>% 
  summarize(engagement_score = sum(engagement_score),
            top_tweet = Tweets[which.max(engagement_score)])

Timeline$Date<- as.Date(Timeline$Date, format = "%Y-%m-%d")

timeline_td <- left_join(x= Timeline, y= thugger_by_day,
                         by = 'Date')
```

```{r fig.height=8, fig.width=10, echo=FALSE}
p <- ggplot(thugger_by_day, aes(x = Date, y = engagement_score)) +
  geom_line(color = 'seagreen') + 
  geom_smooth(method = 'lm', 
              color = 'blue', 
              linetype = 'dashed', 
              se = FALSE) +
  

  geom_point(aes(
    text = paste("Date:", Date, 
                 "<br>Score:", engagement_score, 
                 "<br>Top Tweet:", gsub("(.{40})", "\\1<br>", top_tweet))), 
    color = "seagreen", 
    size = 0.1) +
  

  geom_point(data = na.omit(timeline_td), 
             aes(x = Date,
                 y = engagement_score,
                 text = paste("Date:", Date, 
                              "<br>Score:", engagement_score, 
                              "<br>Event:", gsub("(.{40})", "\\1<br>", Event), 
                              "<br>Top Tweet:", gsub("(.{40})", "\\1<br>", top_tweet))), 
             color = "red", 
             size = 2) +
  
  labs(
    title = 'ThuggerDaily by Point of Interest',
    y = 'Engagement Score',
    x = 'Date'
  ) +
  theme_classic()

ggplotly(p, tooltip = 'text') %>%
  layout(
    hoverlabel = list(
      font = list(size = 21)  # Increase font size for hover tooltips
    ),
    clickmode = "event+select"  # Enable click events for further interaction
  )
```

There is particular trend for ThuggerDaily to tweet before any major even which took place into court the following day or after some few days

## Google Trends

```{r echo=FALSE}
interest_over_time <- read_excel("/Users/sagnikchakravarty/Documents/Young Thug/Data/Cleaned Data/Topic Modeling/Internet/GoogleTrends.xlsx",  sheet = "interest over time")

interest_by_region <-  read_excel("/Users/sagnikchakravarty/Documents/Young Thug/Data/Cleaned Data/Topic Modeling/Internet/GoogleTrends.xlsx" ,sheet = "interest by region")

interest_by_demographics <- read_excel("/Users/sagnikchakravarty/Documents/Young Thug/Data/Cleaned Data/Topic Modeling/Internet/GoogleTrends.xlsx", sheet = 'interest by demographics')
```

```{r echo=FALSE}
scaling_factor <- sum(thugger_by_day$engagement_score) / sum(interest_over_time$hits)
interest_over_time <- interest_over_time %>%
  group_by(keyword) %>%
  mutate(scaled_hits = hits * scaling_factor)

interest_over_time$date <- as.Date(interest_over_time$date)
thugger_by_day$Date <- as.Date(thugger_by_day$Date)

date_range <- range(thugger_by_day$Date)

interest_over_time_filtered <- interest_over_time %>%
  filter(date >= date_range[1] & date <= date_range[2])
thugger_by_day <- thugger_by_day %>%
  mutate(label = "ThuggerDaily")
p1 <- ggplot() +
  geom_line(data = interest_over_time_filtered, 
            aes(x = date, 
                y = scaled_hits, 
                group = keyword, 
                color = keyword)) +
  
  geom_line(data = thugger_by_day, 
            aes(x = Date, 
                y = engagement_score, 
                color = label), 
            inherit.aes = FALSE, 
            size = .5, 
            alpha = 0.3) +
  
  geom_point(data = thugger_by_day,
             aes(x = Date, 
                 y = engagement_score,
                 text = paste("Date:", Date, 
                              "<br>Score:", engagement_score, 
                              "<br>Top Tweet:", gsub("(.{40})", "\\1<br>", top_tweet)),
                 color = label), 
             inherit.aes = FALSE, 
             size = .5) +
  geom_point(data = na.omit(timeline_td), 
             aes(x = Date,
                 y = engagement_score,
                 text = paste("Date:", Date, 
                              "<br>Score:", engagement_score, 
                              "<br>Event:", gsub("(.{50})", "\\1<br>", Event), 
                              "<br>Top Tweet:", gsub("(.{50})", "\\1<br>", top_tweet))), 
             color = "red", 
             size = 2)+
  labs(
    title = "Interest Over Time with Engagement Scores",
    x = "Date",
    y = "Value",
    color = "Legend"
  ) +
  theme_minimal()

ggplotly(p1, tooltip = 'text') %>%
  layout(
    hoverlabel = list(
      font = list(size = 21)  # Increase font size for hover tooltips
    ),
    clickmode = "event+select"  # Enable click events for further interaction
  )
```

## Newspaper

```{r echo=FALSE, results='hide'}
newspaper <- read_csv("/Users/sagnikchakravarty/Documents/Young Thug/Sentiment Analysis/Newspaper/newspaper.csv",  col_types = cols(...1 = col_skip()))

keyword_mapping <- c(
  'young thug' = 'young thug',
  'gunna' = 'gunna',
  'yfn lucci' = 'yfn lucci',
  'yfn' = 'yfn',
  'ysl' = 'ysl',
  'ysl rico' = 'rico',
  'rico' = 'ysl rico',
  'yak gotti' = 'yak gotti',
  'yak' = 'yak gotti',
  'gotti' = 'yak gotti',
  'shannon stillwell' = 'shannon stillwell',
  'shannon' = 'shannon stillwell',
  'stillwell' = 'shannon stillwell',
  'sb' = 'shannon stillwell',
  'jeffrey williams' = 'young thug',
  'jeffrey' = 'young thug',
  'williams' = 'young thug',
  'deamonte kendrick' = 'deamonte kendrick',
  'deamonte' = 'deamonte kendrick',
  'kendrick' = 'deamonte kendrick',
  'sergio kitchens' = 'gunna',
  'sergio' = 'gunna',
  'kitchens' = 'gunna',
  'lil rod' = 'lil rod',
  'rodalius ryan' = 'rodalius ryan',
  'rodalius' = 'rodalius ryan',
  'ryan' = 'rodalius ryan',
  'qua' = 'qua',
  'quamarvious nichols' = 'quamarvious nichols',
  'quamarvious' = 'quamarvious nichols',
  'nichols' = 'quamarvious nichols',
  'christian eppinger' = 'christian eppinger',
  'eppinger' = 'christian eppinger',
  'bhris' = 'bhris',
  'paige reese whitaker' = 'paige reese whitaker',
  'whitaker' = 'paige reese whitaker',
  'ural d. glanville' = 'ural d. glanville',
  'ural glanville' = 'ural glanville',
  'glanville' = 'ural glanville',
  'shukura l. ingram' = 'shukura l. ingram',
  'ingram' = 'shukura l. ingram',
  'brian steel' = 'brian steel',
  'adriane love' = 'adriane love',
  'simone hylton' = 'simone hylton',
  'simone' = 'simone hylton',
  'hylton' = 'simone hylton',
  'thuggerdaily' = 'thuggerdaily',
  'thugger daily' = 'thuggerdaily'
)

# Function to clean and transform the keywords
transform_keywords <- function(df, keywords_column) {
  df %>%
    mutate(
      Keywords = str_split(!!sym(keywords_column), ",\\s*") %>%  # Split keywords by comma
        map(~ unique(str_trim(keyword_mapping[.x] %||% .x))) %>%  # Map and replace, remove duplicates
        map_chr(~ paste(sort(.x), collapse = ", "))  # Sort and combine into a single string
    )
}
```

We will calculate the overall sentiment using the following formula:

$$
\text{Sentiment Score}_{(Headline, Snippet, Article)} =\\ \begin{cases} 1 \times \text{Sentiment Score} & \text{if Sentiment = 'Positive'} \\-1 \times \text{Sentiment Score} & \text{if Sentiment = 'Negative'}\end{cases}
$$

Now we are giving more weight to the sentiment shown in the headlines than the sentiment shown in description or article as most people form opinion about a subject from reading than headlines alone, more over the articles are mostly paywalled in these websites so article are getting the least weight

$$
\text{Overall Sentiment Score} = \frac{0.4\times S_{Headlines}+0.35\times \times S_{Snippets}+0.25\times S_{Article}}{3}
$$

$$
\text{Overall Sentiment} = \begin{cases} Positive, \text{ Overall Sentiment Score}\geq0\\ Negative, \text{ Otherwise} \end{cases}
$$

```{r echo=FALSE}
newspaper <- newspaper %>% mutate(
    score_headline = ifelse(Sentiment_headline == "NEGATIVE", score_headline * -1, score_headline),
    score_snippet = ifelse(Sentiment_snippet == "NEGATIVE", score_snippet * -1, score_snippet),
    score_article = ifelse(Sentiment_article == "NEGATIVE", score_article * -1, score_article)
  ) %>% mutate(overall_sentiment_score = (0.4*score_headline+0.35*score_snippet+0.25*score_article)/3) %>% mutate(overall_sentiment = ifelse(overall_sentiment_score >=0, 'POSITIVE', 'NEGATIVE'))

newspaper <- transform_keywords(newspaper, 'Keywords')
```

```{r}
# Example code to create an interactive plot
newspaper %>%
  filter(!is.na(publication_date) & !is.na(Keywords)) %>%
  separate_rows(Keywords, sep = ",\\s*") %>%
  mutate(month_year = floor_date(as.Date(publication_date), "month")) %>%
  group_by(Keywords, month_year) %>%
  summarize(number_of_articles = n(), .groups = 'drop') %>%
  ggplot(aes(x = month_year, y = number_of_articles, color = Keywords, group = Keywords)) +
  geom_line() +
  labs(title = "Total Number of Articles Published by Keywords",
       x = "Month/Year",
       y = "Number of Articles",
       color = "Keywords") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_viridis(discrete = TRUE, option = "A")-> p

# Convert ggplot to interactive plot using plotly
interactive_plot <- ggplotly(p)

# Create a list of buttons for each keyword
keywords <- unique(newspaper %>%
  filter(!is.na(Keywords)) %>%
  separate_rows(Keywords, sep = ",\\s*") %>%
  pull(Keywords))

# Create a list of visibility settings for each keyword
visibility <- lapply(keywords, function(keyword) {
  list(
    label = keyword,
    method = "relayout",
    args = list(
      "visible", 
      rep(FALSE, length(keywords))  # Set all to FALSE initially
    )
  )
})

# Add "All Keywords" button to show all traces
buttons <- list(
  list(
    label = "All Keywords",
    method = "relayout",
    args = list(
      "visible", 
      rep(TRUE, length(keywords))  # Show all traces
    )
  )
)

# Add the keyword buttons to the list
buttons <- c(buttons, visibility)

# Update the layout with the dropdown menu
interactive_plot <- interactive_plot %>%
  layout(
    updatemenus = list(
      list(
        type = "dropdown",
        x = 0.17,
        xanchor = "left",
        y = 1.15,
        yanchor = "top",
        buttons = buttons
      )
    ),
     legend = list(
    x = 1,  # Position legend to the right
    y = 1,  # Align legend at the top
    xanchor = "left",  # Anchor legend to the left
    yanchor = "top",   # Anchor legend to the top
    orientation = "v",  # Vertical orientation
    font = list(size = 8),  # Reduce legend text size further
    traceorder = "normal",  # Adjust trace order to make it more compact
    itemwidth = 30,  # Adjust item width to make legend more compact
    itemsizing = "constant"  # Ensure the size of legend items are constant
  ),
  xaxis = list(
    tickfont = list(size = 10)  # Reduce x-axis text size
  ),
  yaxis = list(
    tickfont = list(size = 10)  # Reduce y-axis text size
  ),
  margin = list(r = 150)  # Add right margin to prevent legend cutoff
)


interactive_plot

```

```{r echo=FALSE}
p3 <- newspaper %>%
  group_by(Source, overall_sentiment) %>%
  summarize(number_of_newspaper = n(), overall_sentiment_count = n(), .groups = 'drop') %>%
  ggplot(aes(x = Source, 
             y = number_of_newspaper, 
             fill = overall_sentiment,
             text = paste('Source', Source,
                          '<br> Sentiment', overall_sentiment,
                          '<br> Count', number_of_newspaper))) +
  geom_bar(stat = 'identity') +
  labs(title = "Number of Articles by Source", x = "Source", y = "Number of Articles") +
  theme_minimal()

ggplotly(p3, tooltip = 'text')
```

```{r fig.width=15, fig.height=10, echo=FALSE}
p4 <- newspaper %>%
  # Separate keywords into individual rows
  separate_rows(Keywords, sep = ",\\s*") %>%
  group_by(Source, overall_sentiment, Keywords) %>%
  summarize(number_of_newspaper = n(), .groups = 'drop') %>%
  ggplot(aes(x = Source, y = number_of_newspaper, fill = Keywords, 
             text = paste('Source:', Source, 
                          '<br> Sentiment:', overall_sentiment, 
                          '<br> Keywords:', Keywords, 
                          '<br> Count:', number_of_newspaper))) + 
  geom_bar(stat = 'identity', position = 'stack') + 
  facet_wrap(~ overall_sentiment, scales = 'free_y') +  # Separate by sentiment
  labs(title = "Number of Articles by Source and Sentiment", 
       x = "Source", 
       y = "Number of Articles") + 
  theme_minimal()+
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  guides(
   colour = guide_colourbar(order = 1),
   shape = guide_legend(order = 2),
   size = guide_legend(order = 3)
 )
# Convert ggplot to plotly
p4_plotly <- ggplotly(p4, tooltip = 'text')

# Adjust layout to prevent legend cutoff
p4_plotly <- p4_plotly %>% layout(
  legend = list(
    x = 1,  # Position legend to the right
    y = 1,  # Align legend at the top
    xanchor = "left",  # Anchor legend to the left
    yanchor = "top",   # Anchor legend to the top
    orientation = "v",  # Vertical orientation
    font = list(size = 8),  # Reduce legend text size further
    traceorder = "normal",  # Adjust trace order to make it more compact
    itemwidth = 30,  # Adjust item width to make legend more compact
    itemsizing = "constant"  # Ensure the size of legend items are constant
  ),
  xaxis = list(
    tickfont = list(size = 10)  # Reduce x-axis text size
  ),
  yaxis = list(
    tickfont = list(size = 10)  # Reduce y-axis text size
  ),
  margin = list(r = 150)  # Add right margin to prevent legend cutoff
)

# Display the plot
p4_plotly
```

```{r}
newspaper
```
